Carbonate chemistry at Ny-Ålesund

### 2022-02-24 awipev-CO2.Rmd
testing greek in facet labels (2950)

```{r pH and CT with all K1K2 using pCO2-AT, echo=FALSE, warning=FALSE, message=FALSE}
tmp <- d_all %>% 
  dplyr::select(datetime, pco2_fb, at, sal_fb_mix, temp_fb) %>% 
  tidyr::drop_na(pco2_fb, at, sal_fb_mix, temp_fb) %>% 
# This is an important adjustement for pco2_fb on 2019-06-07 09:00:00
# it is too high compared with ph_s_dur. Looking at the dygraph suggests that there has been a peak just before that time and that the values were coming back down. This is this in accordance with pco2_calc_fb calculated from 
dplyr::mutate(pco2_fb = ifelse(datetime == as.POSIXct("2019-06-07 09:00:00"), 203, pco2_fb))
# Using Lueker  
carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", 
               pHscale = "T", b = "u74")
# normalize Lueker-derived pH at 4°C
carb_l$pH <- pHinsi(pH = carb_l$pH, ALK = carb_l$ALK, Tinsi = 4, Tlab = carb_l$T, Pinsi = 0, 
                         S = carb_l$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
                         pHscale = "T", b="u74")
# Using Sulpis
carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks = "d", 
               pHscale = "T", b = "u74")
# normalize Sulpis-derived pH at 4°C
carb_s$pH <- pHinsi(pH = carb_s$pH, ALK = carb_s$ALK, Tinsi = 4, Tlab = carb_s$T, Pinsi = 0, 
                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
                         pHscale = "T", b="u74")
# Using Papadimitriou
carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks = "d", 
               pHscale = "T", b = "u74")
# normalize Papadimitriou-derived pH at 4°C
carb_p$pH <- pHinsi(pH = carb_p$pH, ALK = carb_p$ALK, Tinsi = 4, Tlab = carb_p$T, Pinsi = 0, 
                         S = carb_p$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
                         pHscale = "T", b="u74")
# Using Millero et al. (2002)
carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks = "d", 
               pHscale = "T", b = "u74")
# normalize Millero et al. (2002)-derived pH at 4°C
carb_m$pH <- pHinsi(pH = carb_m$pH, ALK = carb_m$ALK, Tinsi = 4, Tlab = carb_m$T, Pinsi = 0, 
                         S = carb_m$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
                         pHscale = "T", b="u74")
# calculate difference Lueker - Sulpis
diff_ls <- as_tibble(carb_l - carb_s) %>% 
  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
  dplyr::mutate(deltas = "L-S", .before = 1)
# calculate difference Lueker - Papadimitriou
diff_lp <- as_tibble(carb_l - carb_p) %>% 
  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
  dplyr::mutate(deltas = "L-P", .before = 1)
# calculate difference Lueker - Millero
diff_lm <- as_tibble(carb_l - carb_m) %>% 
  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
  dplyr::mutate(deltas = "L-M", .before = 1)
# bind and plot
diff_all <- dplyr::bind_rows(diff_ls, diff_lp, diff_lm) %>% 
  dplyr::mutate(delta_ct = delta_ct * 1e6)
diff_all_long <- diff_all %>% 
  tidyr::pivot_longer(-deltas, names_to = "variable") %>% 
  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'pH' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))

p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L-S', 'L-P', 'L-M'), y=value))+
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  geom_hline(yintercept = 0) +
  labs(title = "", x = "", y= "") +
  facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
  Mytheme(size_labs = 10)
p
diff_all_long$variable <- factor(diff_all_long$variable, levels = c('C[T]','Omega[a]', 'pH'))
fct_relevel(diff_all_long$variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite')

>>>>

```{r pH and CT with all K1K2 using pCO2-AT, echo=FALSE, warning=FALSE, message=FALSE}
tmp <- d_all %>% 
  dplyr::select(datetime, pco2_fb, at, sal_fb_mix, temp_fb) %>% 
  tidyr::drop_na(pco2_fb, at, sal_fb_mix, temp_fb) %>% 
# This is an important adjustement for pco2_fb on 2019-06-07 09:00:00
# it is too high compared with ph_s_dur. Looking at the dygraph suggests that there has been a peak just before that time and that the values were coming back down. This is this in accordance with pco2_calc_fb calculated from 
dplyr::mutate(pco2_fb = ifelse(datetime == as.POSIXct("2019-06-07 09:00:00"), 203, pco2_fb))
# Using Lueker  
carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", 
               pHscale = "T", b = "u74")
# normalize Lueker-derived pH at 4°C
carb_l$pH <- pHinsi(pH = carb_l$pH, ALK = carb_l$ALK, Tinsi = 4, Tlab = carb_l$T, Pinsi = 0, 
                         S = carb_l$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
                         pHscale = "T", b="u74")
# Using Sulpis
carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks = "d", 
               pHscale = "T", b = "u74")
# normalize Sulpis-derived pH at 4°C
carb_s$pH <- pHinsi(pH = carb_s$pH, ALK = carb_s$ALK, Tinsi = 4, Tlab = carb_s$T, Pinsi = 0, 
                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
                         pHscale = "T", b="u74")
# Using Papadimitriou
carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks = "d", 
               pHscale = "T", b = "u74")
# normalize Papadimitriou-derived pH at 4°C
carb_p$pH <- pHinsi(pH = carb_p$pH, ALK = carb_p$ALK, Tinsi = 4, Tlab = carb_p$T, Pinsi = 0, 
                         S = carb_p$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
                         pHscale = "T", b="u74")
# Using Millero et al. (2002)
carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks = "d", 
               pHscale = "T", b = "u74")
# normalize Millero et al. (2002)-derived pH at 4°C
carb_m$pH <- pHinsi(pH = carb_m$pH, ALK = carb_m$ALK, Tinsi = 4, Tlab = carb_m$T, Pinsi = 0, 
                         S = carb_m$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
                         pHscale = "T", b="u74")
# calculate difference Lueker - Sulpis
diff_ls <- as_tibble(carb_l - carb_s) %>% 
  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
  dplyr::mutate(deltas = "L00-S20", .before = 1)
# calculate difference Lueker - Papadimitriou
diff_lp <- as_tibble(carb_l - carb_p) %>% 
  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
  dplyr::mutate(deltas = "L00-P18", .before = 1)
# calculate difference Lueker - Millero
diff_lm <- as_tibble(carb_l - carb_m) %>% 
  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
  dplyr::mutate(deltas = "L00-M02", .before = 1)
# bind and plot
diff_all <- dplyr::bind_rows(diff_ls, diff_lp, diff_lm) %>% 
  dplyr::mutate(delta_ct = delta_ct * 1e6)
diff_all_long <- diff_all %>% 
  tidyr::pivot_longer(-deltas, names_to = "variable") %>% 
  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, "'Delta" pH"' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))

p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  geom_hline(yintercept = 0) +
  labs(title = "", x = "", y= "") +
  facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
  Mytheme(size_labs = 10)
p
# diff_all_long$variable <- factor(diff_all_long$variable, levels = c('C[T]','Omega[a]', 'pH'))
# fct_relevel(diff_all_long$variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite')
